### 2021-03-06 article/paper_eng.tex
fixed typos

SNN's local learning rules are significantly understudying in comparison to ANNs, and because of this, SNN-based alrorithms produce lower inference quality metrics. Thus, the study of SNN learning algorithms, like spike-timing-dependent-plasticity (STDP), for use in various SNN architectures is an important problem.

@@

\section*{Keywords}
Spiking Neural Networks, Unsupervised Learning, Ingibitory Connections, Neuroscience

>>>>

SNN's local learning rules are significantly understudied in comparison to ANNs, and because of this, SNN-based alrorithms produce lower inference quality metrics. Thus, the study of SNN learning algorithms, like spike-timing-dependent-plasticity (STDP), for use in various SNN architectures is an important problem.

@@

\section*{Keywords}
Spiking Neural Networks, Unsupervised Learning, Inhibitory Connections, Neuroscience
